---
title: 資料圖像化
output: html_document
author: 趙文
---
<h2 id = 0></h2>
# 目錄
一、 [Search Data](#1)  
二、 [Make a map](#2)  
三、 [Bar Chart Test](#3) 
四、 [Line Chart Test](#4)

<h2 id = 1></h2>
># **一、Search Data**

1. [load data](#1.1)
2. [see origin data](#1.2)
3. [install packages dplyr](#1.3)
4. [tidy Data](#1.4)
5. [see All](#1.5)

<h2 id = 1.1></h2>
>>## 1. load data
```{r}
setwd("/Users/zhaowen/Desktop/Data-Science")
Birth <- read.csv("Birth_rate103-107.csv")
Marry <- read.csv("Marriage_rate103-107.csv")
```

<h2 id = 1.2></h2>
>>## 2. see origin data
```{r}
head(Birth,2)
head(Marry,2)
```

<h2 id = 1.3></h2>
>>## 3. install packages dplyr
```{r}
library(dplyr)
All <- cbind(Birth, Marry)
```

<h2 id = 1.4></h2>
>>## 4. tidy Data
```{r}
All <- All[,-c(13,14)]
```

<h2 id = 1.5></h2>
>>## 5. see All
```{r}
head(All)
```



<h2 id = 2></h2>
># **二、Make a map**

1. [input shape files](#2.1)
2. [select administration in taipei](#2.2)
3. [create data plot on map](#2.3)
4. [fortify shapefile to get into dataframe](#2.4)
5. [merge to map & data gether](#2.5)
6. [basic plot](#2.6)

<h2 id = 2.1></h2>
>>## 1. input shape files
```{r}
setwd("/Users/zhaowen/Desktop/Data-Science/mapdata201906180922")
library(maptools)
Ad.shp <- readShapeSpatial("TOWN_MOI_1080617.shp")
```

<h2 id = 2.2></h2>
>>## 2. select administration in taipei
```{r}
Ad.taipei <- Ad.shp[which(Ad.shp@data$COUNTYNAME == "臺北市"), ]
names(Ad.taipei)
head(Ad.taipei,2)
print(Ad.taipei$TOWNNAME)
```

<h2 id = 2.3></h2>
>>## 3. create data plot on map
```{r}
Ad.num <- length(Ad.taipei$TOWNNAME)
mydata <- data.frame(Ad.taipei$TOWNNAME, id=(1:Ad.num), prevalence = rnorm(Ad.num, 55, 5))
head(mydata)
```

<h2 id = 2.4></h2>
>>## 4. fortify shapefile to get into dataframe
```{r}
library(ggplot2)
Ad.taipei.df <- fortify(Ad.taipei, region = "TOWNID")
class(Ad.taipei.df)
head(Ad.taipei.df,12)
```
到這一步開始有問題，嘗試過後還沒有辦法解決（努力中⋯⋯）

<h2 id = 2.5></h2>
>>## 5. merge to map & data gether

<h2 id = 2.6></h2>
>>## 6. basic plot
```{r}

```


<h2 id = 3></h2>
># **三、Bar Chart Test**

1. [data in](#3.1)
2. [bar chart](#3.2)

<h2 id = 3.1></h2>
>>## 1. data in
```{r}
library(dplyr)
birth_bar <- All %>%
  select(year, location, 育齡婦女一般生育率) %>%
  filter(year %in% c("107年"))
```

<h2 id = 3.2></h2>
>>## 2. bar chart
```{r}
ggplot(data = birth_bar,
       aes(x=location,
           y=育齡婦女一般生育率,
           fill="育齡婦女一般生育率"))+
  geom_bar(stat="identity")
```


<h2 id = 4></h2>
># **四、Line Chart Test**

1. [data in](#4.1)
2. [line chart](#4.2)

<h2 id = 4.1></h2>
>>## 1. data in
```{r}
library(ggplot2)
birth_line <- All %>%
  select(year, location, 育齡婦女一般生育率) %>%
  filter(location %in% c("總計"))
head(birth_line)
```

<h2 id = 4.2></h2>
>>## 2. line chart
```{r}
ggplot(data = birth_line,
       aes(x= "year", 
           y= "育齡婦女一般生育率",
           group=1))+
  geom_line()+
  geom_point()
```

[back to top](#0)